Different forms of uncertainty differently affect the evolution of social learning

### 2022-10-09 meanNetPayoffs.tex
updated figures and converted to natbib

    \begin{center}
      \includegraphics[width=1.25in]{Figures/legendElements/solid.pdf}
      {\Huge Simulations} \quad \quad 
      \includegraphics[width=1.25in]{Figures/legendElements/ldash.pdf}
      {\Huge$\meanasoc$} \quad \quad 
      \includegraphics[width=1.25in]{Figures/legendElements/dot.pdf}
      {\Huge$\meansoc$} \quad \quad
      \includegraphics[width=1.25in]{Figures/legendElements/ldashdot.pdf}
      {\Huge$\meanasoc = \meansoc$}
    \end{center}
\end{document}

>>>>

    \begin{center}
      {\Huge \textbf{+} \huge Location where homogenous social and asocial payoffs
      are equal} \quad \quad 
    \end{center}

\end{document}
